---
title: "Lek-Paradox Second Draft"
author: "LRM"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: FALSE
    toc_float: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Update Keys
gitcreds::gitcreds_set()

#This is all Major WIP


##Model Overview
#Lek Paradox Second Draft
#Make a new Model with updated Ideas
#Make a female choose male model in which there arent a female prefences explictly set nor any thresholds.
#This model assumes extreme polygeny. Many women choose 1 man
#Instead, have equal numbers of males/females OR random, Each agent having an ID associated.
#Assign sex values either 1 or 0. 
#Each agent has a trait value assigned via a genetics system.
#A seperate vector containing each agents ID value would be assigned a 0 or 1 loci value from L1 to L100
#Can be assigned via, rbinom(100,1,0.5) IN OTHER WORDS, ID of 100 to 1 given a 50% chance to be assigned a 1 or 0 in each loci value>
#Trait values per agent is decided through the sum of all loci values from the genetics system vector.
#FROM THERE, since many females are given the abilty to mate with 1 male, this is decided through which available male 
#has the highest trait value from the sum of the loci values in the genetic system vector.
#IE  0=Female 1=Male 
#ID SEX TRAIT       ID    GENETIC SYSTEM L1 L2 L3 L4 L5.... L100
#1   0    70        1                     0 1  0  1  0      0 
#2   0    60        2                     1
#3   0    30        3
#4   1    0         4
#5   1    10        5
#6   1    50        6

##Purpose##
#To see in a primarliy polygenous species how a males mate value mixed with the multiple females genetic varience, produce offspring with either a highly varied trait value profile or produce a similar/linear trait value generation via evolution (IE Genetic Run Off)
##Agents
```{r agents}



```

##Life Cycle
```{r lifeCycle}

```


##Assess
```{r assess}

```


##Analysis
```{r analysis}

```

##Model
```{r model}

```


##Packages
```{r packages}

library(ggplot2)

```


##Parameters
```{r parameters}

popSize <- 6

```



##Functions
```{r functions}

agentGenerate <- function(popSize){
  
  
  ID<-1:popSize
  
  #Assign each agent a random Gender #Sample chooses random option
  sex <- rep(c("Male","Female"),each = popSize/2)
  
  #male <- sample(c)
  #female <- 1
  
  genetics <- rbinom(popSize,100,0.5)


  #Pretty sure these are the same things just written differently
  traitValueMale <- sample(genetics,popSize,replace=T)
  traitValueFemale <- sample(rbinom(popSize,100,0.5),popSize,replace=T)
  
  

  #Generate agents
  agents <- data.frame(ID,sex,genetics,traitValueMale,traitValueFemale)
  
  #Return Agents
  return(agents)
}

#For Reproductibility?
set.seed(01)

#Stores First Gen Agent Data
agents_data<-data.frame(agentGenerate(popSize))
#Vector that stores agents Loci values from 1 to 100
  #storedGenetics<- rep(NA,nrow(agents*100))
  

#TO CHECK IF A VECTOR IS ATOMIC
is.atomic(agents$ID)

#Sus out the highest trait value and male (potential problem, 2 males with the same value)
maleAgentsData <- agents_data[agents_data$sex == "Male",]
chosenMale <- maleAgentsData$ID[which.max(maleAgentsData$traitValueMale)]
max_traitValueMale <- max(maleAgentsData$traitValueMale)

femaleAgentsData <- agents_data[agents_data$sex == "Female",]

#Ignores Missing Values
#na.rm = T

totalOffspring <-(popSize)

reproduction <- function (femaleAgentsData, maleAgentsData,totalOffspring){
  
  
  
  #get the maximum ID available for both male and female agents
  maxID <- max(c(max(femaleAgentsData$ID, na.rm = T), max(maleAgentsData$ID, na.rm = T)))
  
  offspring <- data.frame(
    #Get the Latest ID, add 1, to get the next level of offspring ID.
   ID <- seq(maxID + 1,maxID+totalOffspring),
   #create Male and Female offspring of each until half of the total is met
   sex <- rep(c("Male", "Female"), each = totalOffspring/2),
   #Genetics System from Prior function
   genetics = rbinom(totalOffspring, 100, 0.5),
   #Create code so that 1 mal
   traitValueMale <- ifelse(rep(c("Male","Female"),each=totalOffspring/2)== "Male", max_traitValueMale, rep(max(maleAgentsData$traitValueMale, na.rm = TRUE),totalOffspring)),
   traitValueFemale <- sample(femaleAgentsData$traitValueFemale, totalOffspring, replace = T)
  )
  
  #Return offsprings
  return(offspring)
}

femaleAgents <- agents_data[agents_data$sex == "Female",]
maleAgents <- agents_data[agents_data$sex == "Male",]



#Mating Process
offspring <- reproduction(femaleAgentsData, maleAgentsData,totalOffspring)

##Mating Process
#mate <- function(popSize){
 # if
#}   

```






###Give meaning to loci values??????



```{r}

```

